### 2023-03-24 reachable-resilience.tex
up

Unfortunately, resilience is undecidable for (general) WSTS even with strong monotony.
This stems from the fact that $t$-liveness is undecidable for reset Petri-Nets.

@@

Since $t$-liveness is undecidable for reset Petri-Nets that are WSTS with strong monotony, from Proposition \ref{reductions},  we deduce that resilience is undecidable for WSTS with strong monotony.

\begin{theorem}
{\sc resilience} is undecidable for WSTS with strong monotony.
\end{theorem}

\begin{proposition}
In WSTS with strong monotony, the bounded resilience problem is
reducible to the $k$-resilience problem.
\end{proposition}

@@

\begin{proposition}
In WSTS with strong monotony, the bounded resilience problem is
equivalent to the resilience problem.
\end{proposition}

@@

\begin{corollary}
Bounded Resilience is undecidable for WSTS with strong monotony.
\end{corollary}

@@

Let us deduce that effective basis of $post^*$ ex reset PN ?

Since VASS are WSTS with strong upward compatibility and since there is an algorithm that computes a finite basis of  $\uparrow post^*(S)$, \cite{DBLP:conf/gg/Ozkan22} deduced that bounded resilience is decidable for VASS, hence resilience is decidable for VASS. \alain{resilience decidable for LCS ? LCS sont-ils strong (quelle sémantique ?) et $\uparrow post^*(S)$ is computable ?}

>>>>

Unfortunately, reachable-resilience is undecidable for (general) WSTS even with strong monotony.
This stems from the fact that $t$-liveness is undecidable for reset Petri-Nets.

@@

Since $t$-liveness is undecidable for reset Petri-Nets that are WSTS with strong monotony, from Proposition \ref{reductions},  we deduce that reachable-resilience is undecidable for WSTS with strong monotony.

\begin{theorem}
{\sc reachable-resilience} is undecidable for WSTS with strong monotony.
\end{theorem}

\begin{proposition}
In WSTS with strong monotony, the bounded reachable-resilience problem is
reducible to the $k$-reachable-resilience problem.
\end{proposition}

@@

\begin{proposition}
In WSTS with strong monotony, the bounded reachable resilience problem is
equivalent to the reachable-resilience problem.
\end{proposition}

@@

\begin{corollary}
Bounded reachable-resilience and 
$k$ reachable-resilience are undecidable for WSTS with strong monotony.
\end{corollary}

@@

% Let us deduce that effective basis of $post^*$ ex reset PN ?

Since VASS are WSTS with strong upward compatibility and since there is an algorithm that computes a finite basis of  $\uparrow post^*(S)$, \cite{DBLP:conf/gg/Ozkan22} deduced that bounded reachable-resilience is decidable for VASS, hence reachable-resilience is decidable for VASS. \alain{resilience decidable for LCS ? LCS sont-ils strong (quelle sémantique ?) et $\uparrow post^*(S)$ is computable ?}
